Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-05-26 publication_materials/ms_rbc.tex
appendix D: eigenfunctions
G chini and G vassil's feedback

Others have turned to studying quasilinear systems.
The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
This approximation neglects the nonlinear interactions between perturbations which modify the perturbations themselves \cite{marston2016}.
This renders the perturbation equations linear.
Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
In \citet{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.

In this paper we derive and solve a quasilinear form of the Rayleigh-B\'{e}nard convection problem using a similar time scale separation argument.
In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we describe how we evolve the background temperature profile while maintaining marginal stability.
Section~\ref{sec:properties} describes the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
Finally, we describe the results of simulations initialized with marginally-stable thermal equilibria in section~\ref{sec:sims}, and conclude in section~\ref{sec:Discussion}.

@@

@@

\onecolumngrid
\section{MSTE Parameters and Results}\label{sec:tables}

@@

\twocolumngrid

% \bibliographystyle{plain}
\bibliography{he}

>>>>

Others have turned to studying quasilinear systems.
The quasilinear approximation starts with a decomposition of all variables into a background and perturbations about this background.
This approximation neglects the nonlinear interactions between perturbations which modify the perturbations themselves \cite{marston2016}.
This renders the perturbation equations linear.
Although the quasilinear approximation greatly simplifies the problem, an additional condition must be imposed to determine the amplitude of the perturbations.
In \citet{Beaume_2015}, researchers compute ECS in parallel shear flows by deriving and solving a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. 
They assume the background velocity evolves on a slow time scale, and, to determine the perturbation amplitudes, they require marginal stability at each timestep.
% A similar strategy is employed by \citet{michel_chini_2019} to study acoustic streaming.
% In that work, an analytic expression for the first-order perturbation's amplitude is found by deriving a solvability condition.
This quasilinear approach, which relies on multiple scales arguments in conjunction with a marginal stability constraint, is generalized by \cite{Chini_ql}.
Studying two somewhat generic systems, researchers observe interdependent evolution of a background state and its perturbations within a marginally-stable manifold.

In this paper employ the same strategy to the more complicated Rayleigh-B\'{e}nard convection problem.
In section~\ref{sec:model} we recall the underlying equations, and in section~\ref{sec:evolution} we describe how we evolve the background temperature profile while maintaining marginal stability.
Section~\ref{sec:properties} describes the properties of the marginally-stable thermal equilibria, in particular how the Nusselt number and characteristic wavenumbers vary with the Rayleigh number.
Finally, we describe the results of simulations initialized with marginally-stable thermal equilibria in section~\ref{sec:sims}, and conclude in section~\ref{sec:Discussion}.

@@

The temperature boundary layers of MSTE with various $\Ra$ exhibit self-similarity. 
We illustrate this in Figure~\ref{fig:b0_delta} where the mean temperature $\overline{T}$ is plotted along a re-scaled $z$-coordinate.
$\Delta$ denotes the minimum $z$-offset from the boundary layer which satisfies
\begin{equation*}
    \overline{T}|_{z = \Delta} = 0.
\end{equation*}
However $\Delta$ depends only on $\Ra$, effectively being constrained by marginal-stability.
This suggests the re-scaled boundary layer geometry is intrinsic to MSTE, possibly minimizing diffusion as previously hypothesized.

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{b0_delta.pdf}
    \caption{Temperature boundary layer geometries of various MSTE. 
    $\Delta$ denotes the minimum $z$-offset away from the boundary at which the mean temperature changes sign, i.e.~$\overline{T}(1/2 + \Delta) = 0$. 
    Rescaling according to this quantity reveals self-similarity in the temperature boundary layers despite large changes in $\Ra$.}
    \label{fig:b0_delta}
\end{figure}

@@

\onecolumngrid
\section{MSTE Properties, Parameters, and Results}\label{sec:tables}

@@

% \section{MSTE Eigenfunctions}\label{sec:eigenfunctions}
\begin{figure}
    \centering
    \includegraphics[width=7.1in]{grid_vars.pdf}
    \caption{The real and imaginary components of the temperature and pressure MSTE eigenfunctions are illustrated in separate plots for various marginally-stable modes. 
    For the large-scale $k_x = 1.5\pi$ mode, we find the vertical velocity eigenfunction $W$ is maximized near the center of the domain.
    In both other cases ($k_x = 5.5\pi, \, 17.5\pi$) the vertical velocity is localized near the boundaries.
    In the temperature eigenfunction $\Theta$, small-scale zig-zags appear near the boundaries at $k_x = 1.5\pi$, subsiding as $k_x$ increases.}%
    \label{fig:eigenfunctions}%
\end{figure}

\twocolumngrid
\clearpage
% \bibliographystyle{plain}
\bibliography{he}
